PDBF Documentation

### 2015-07-06 Documentation.tex
finished dataText

\noindent We extended AlaSQL with the following statistical sql functions:\\[5pt]
\verb|GRUBBS_FILTER(arr, alpha)|: \\
\indent Desc.: Filters an array of values with a \href{http://en.wikipedia.org/wiki/Grubbs'_test_for_outliers}{grubbs test}\\
\indent Returns the filtered array.\\[3pt]
\indent \option
{arr}
{Array on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}
\indent \option
{alpha}
{significance level}
{Number $>$ 0 AND Number $<$ 1}
{\texttt{0.05}}\\[3pt]
%
\verb|MEAN(arr)|: \\
\indent Desc.: Calculates the \href{http://en.wikipedia.org/wiki/Arithmetic_mean}{arithmetic mean} of an array of values.\\
\indent Returns the arithmetic mean of the array.\\[3pt]
\indent \option
{arr}
{Array on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}\\[3pt]
%
\verb|STDDEV_SAMP(arr)|: \\
\indent Desc.: Calculates the \href{http://en.wikipedia.org/wiki/Standard_deviation}{ sample standard deviation} of an array of values.\\
\indent Returns the sample standard deviation of the array.\\[3pt]
\indent \option
{arr}
{Array on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}\\[3pt]
%
\verb|MARGIN_OF_ERROR(arr, alpha)|: \\
\indent Desc.: Calculates the \href{http://en.wikipedia.org/wiki/Margin_of_error}{margin of error} of an array of values.\\
\indent Returns the margin of error of the array.\\[3pt]
\indent \option
{arr}
{Array on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}
\indent \option
{alpha}
{significance level}
{Number $>$ 0 AND Number $<$ 1}
{\texttt{0.05}}\\[3pt]
%
\verb|CONF_INT(arr, alpha)|: \\
\indent Desc.: Calculates the \href{http://en.wikipedia.org/wiki/Confidence_interval}{confidence interval} of an array.\\
\indent Returns the confidence interval of the array.\\[3pt]
\indent \option
{arr}
{Array on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}
\indent \option
{alpha}
{significance level}
{Number $>$ 0 AND Number $<$ 1}
{\texttt{0.05}}\\[3pt]
%
\verb|T_TEST(arr1, arr2, alpha)|: \\
\indent Desc.: Performs a \href{http://en.wikipedia.org/wiki/Student's_t-test}{Student's t-test} on two arrays.\\
\indent Returns true if they are indistinguishable, and returns false otherwise.\\[3pt]
\indent \option
{arr1, arr2}
{Arrays on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}
\indent \option
{alpha}
{significance level}
{Number $>$ 0 AND Number $<$ 1}
{\texttt{0.05}}\\[3pt]
%
\verb|WELCH_TEST(arr1, arr2, alpha)|:\\
\indent Desc.: Performs a \href{http://en.wikipedia.org/wiki/Welch's_t_test}{Welch's t-test} on two arrays.\\
\indent Returns true if they are indistinguishable, and returns false otherwise.\\[3pt]
\indent \option
{arr1, arr2}
{Arrays on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}
\indent \option
{alpha}
{significance level}
{Number $>$ 0 AND Number $<$ 1}
{\texttt{0.05}}\\[3pt]
%
\section{Sql data sources}
\noindent Macros: \\[3pt]
\verb|\dbSQLText{sqlQueryString}| \\
\verb|\dbSQLFile{fileWithSqlQueries}| \\
\verb|\dbSQLJDBC{jdbcConnectionURL}{user}{password}{commaSeperatedListOfTableNames}| \\
\textbf{Note:} jdbcConnectionURL consist of jdbc followed by the name of the dbms (currently only postgresql and mysql are supported) followed by the url of the dbms followed by the database name (e.g. jdbc:postgresql://localhost:5432/postgres).\\
\textbf{Note:} jdbcConnectionURL, user, and password are not stored in the output document.

@@

\option %TODO: not yet implemented
{logscale}
{If set, the y axis uses log scale. Can also be redefined globally (\texttt{pdbfLogscale}).}
{\texttt{true} or \texttt{false}}
{\texttt{false}}

\option %TODO: not yet implemented
{overlap}
{Unused.}
{\texttt{TODO: ...}}
{\texttt{TODO: ...}}

\option %TODO: not yet implemented
{legendpos}
{Sets the position of the legend of the chart.}
{\texttt{TODO: ...}}
{\texttt{TODO: ...}}

\option %TODO: not yet implemented
{includeZero}
{Set the minimum of the range of the y-axis to zero.}
{\texttt{true} or \texttt{false}}
{\texttt{false}}

\option %TODO: not yet implemented
{drawPoints}
{Whether to show each point in line.}
{\texttt{true} or \texttt{false}}
{\texttt{false}}

\option %TODO: not yet implemented
{fillGraph}
{Whether to fill the area below the graph.}
{\texttt{true} or \texttt{false}}
{\texttt{false}}

\option %TODO: not yet implemented
{showRangeSelector}
{Whether to show a range selector for the x-axis below the chart.}
{\texttt{true} or \texttt{false}}
{\texttt{false}}

@@

\newpage
\subsection{Sql}
Example:\\[3pt]
\sql{SELECT * FROM test;}\\[3pt]
%
\noindent Macros: \\[3pt]
\verb|\sql[textForPage]{queryForOverlay}| \\
\textbf{Note:} if \verb|textForPage| is omitted the \verb|queryForOverlay| is used as text for the page.\\[8pt]

\section{F.A.Q.}
\begin{itemize}
\item Q.: The overlay is not on the right position.\\
A.: Most likely you use pages with different sizes in your document. This is currently not supported by PBDF 
\item Q.: I get \verb|Error: paperwidth value missing! Did you forgot to specify the| \\ \verb|papersize via the geometry package?| when compiling my document.\\
A.: You need to explicitly specify the papersize of your document via the geometry package (e.g. \verb|\usepackage[letterpaper]{geometry}|)
\item Q.: I get \verb|\unhbox \voidb@x \bgroup \let \unhbox \voidb@x \setbox \@tempboxa \hbox| \verb|{u\global \mathchardef \accent@spacefactor \spacefactor }\accent 127 u\egroup| \newline \verb|\spacefactor \accent@spacefactor| or a similar string in a error message.\\
A.: Chances are high that you use the \verb|\usepackage[utf8]{inputenc}| package or a similar package. These are not fully compatible with PDBF. If you really have to use the utf8 package then you cant use special characters inside PDBF commands.
\end{itemize}

>>>>

\noindent We extended AlaSQL with the following statistical sql functions:\\[5pt]
\verb|GRUBBS_FILTER(arr, alpha)|: \\
\indent Desc.: Filters an array of values with a \href{http://en.wikipedia.org/wiki/Grubbs'_test_for_outliers}{grubbs test}\\
\indent Returns the filtered array.\\[3pt]
\indent \option
{arr}
{Array on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}
\indent \option
{alpha}
{significance level}
{Number $>$ 0 AND Number $<$ 1}
{\texttt{0.05}}\\[3pt]
%
\verb|MEAN(arr)|: \\
\indent Desc.: Calculates the \href{http://en.wikipedia.org/wiki/Arithmetic_mean}{arithmetic mean} of an array of values.\\
\indent Returns the arithmetic mean of the array.\\[3pt]
\indent \option
{arr}
{Array on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}\\[3pt]
%
\verb|STDDEV_SAMP(arr)|: \\
\indent Desc.: Calculates the \href{http://en.wikipedia.org/wiki/Standard_deviation}{ sample standard deviation} of an array of values.\\
\indent Returns the sample standard deviation of the array.\\[3pt]
\indent \option
{arr}
{Array on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}\\[3pt]
%
\verb|MARGIN_OF_ERROR(arr, alpha)|: \\
\indent Desc.: Calculates the \href{http://en.wikipedia.org/wiki/Margin_of_error}{margin of error} of an array of values.\\
\indent Returns the margin of error of the array.\\[3pt]
\indent \option
{arr}
{Array on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}
\indent \option
{alpha}
{significance level}
{Number $>$ 0 AND Number $<$ 1}
{\texttt{0.05}}\\[3pt]
%
\verb|CONF_INT(arr, alpha)|: \\
\indent Desc.: Calculates the \href{http://en.wikipedia.org/wiki/Confidence_interval}{confidence interval} of an array.\\
\indent Returns the confidence interval of the array.\\[3pt]
\indent \option
{arr}
{Array on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}
\indent \option
{alpha}
{significance level}
{Number $>$ 0 AND Number $<$ 1}
{\texttt{0.05}}\\[3pt]
%
\verb|T_TEST(arr1, arr2, alpha)|: \\
\indent Desc.: Performs a \href{http://en.wikipedia.org/wiki/Student's_t-test}{Student's t-test} on two arrays.\\
\indent Returns true if they are indistinguishable, and returns false otherwise.\\[3pt]
\indent \option
{arr1, arr2}
{Arrays on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}
\indent \option
{alpha}
{significance level}
{Number $>$ 0 AND Number $<$ 1}
{\texttt{0.05}}\\[3pt]
%
\verb|WELCH_TEST(arr1, arr2, alpha)|:\\
\indent Desc.: Performs a \href{http://en.wikipedia.org/wiki/Welch's_t_test}{Welch's t-test} on two arrays.\\
\indent Returns true if they are indistinguishable, and returns false otherwise.\\[3pt]
\indent \option
{arr1, arr2}
{Arrays on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}
\indent \option
{alpha}
{significance level}
{Number $>$ 0 AND Number $<$ 1}
{\texttt{0.05}}\\[3pt]
%
\section{Sql data sources}
\noindent Macros: \\[3pt]
\verb|\dbSQLText{sqlQueryString}| \\
\verb|\dbSQLFile{fileWithSqlQueries}| \\
\verb|\dbSQLJDBC{jdbcConnectionURL}{user}{password}{commaSeperatedListOfTableNames}| \\
\textbf{Note:} jdbcConnectionURL consist of jdbc followed by the name of the dbms (only postgresql and mysql are currently supported) followed by the url of the dbms followed by the database name (e.g. jdbc:postgresql://localhost:5432/postgres).\\
\textbf{Note:} jdbcConnectionURL, user, and password are not stored in the output documents.

@@

%\option %TODO: not yet implemented
%{logscale}
%{If set, the y axis uses log scale. Can also be redefined globally (\texttt{pdbfLogscale}).}
%{\texttt{true} or \texttt{false}}
%{\texttt{false}}
%
%\option %TODO: not yet implemented
%{overlap}
%{Unused.}
%{\texttt{TODO: ...}}
%{\texttt{TODO: ...}}
%
%\option %TODO: not yet implemented
%{legendpos}
%{Sets the position of the legend of the chart.}
%{\texttt{TODO: ...}}
%{\texttt{TODO: ...}}
%
%\option %TODO: not yet implemented
%{includeZero}
%{Set the minimum of the range of the y-axis to zero.}
%{\texttt{true} or \texttt{false}}
%{\texttt{false}}
%
%\option %TODO: not yet implemented
%{drawPoints}
%{Whether to show each point in line.}
%{\texttt{true} or \texttt{false}}
%{\texttt{false}}
%
%\option %TODO: not yet implemented
%{fillGraph}
%{Whether to fill the area below the graph.}
%{\texttt{true} or \texttt{false}}
%{\texttt{false}}
%
%\option %TODO: not yet implemented
%{showRangeSelector}
%{Whether to show a range selector for the x-axis below the chart.}
%{\texttt{true} or \texttt{false}}
%{\texttt{false}}

@@

\subsection{Sql}
Example:\\[3pt]
\sql{SELECT * FROM test;}\\[3pt]
%
\noindent Macros: \\[3pt]
\verb|\sql[textForPage]{queryForOverlay}| \\
\textbf{Note:} if \verb|textForPage| is omitted the \verb|queryForOverlay| is used as text for the page.\\[8pt]

\noindent Options: \\[3pt]

\option
{color}
{The textcolor of the displayed text.}
{\texttt{white}, \texttt{black}, \texttt{red}, \texttt{green}, \texttt{blue}, \texttt{cyan}, \texttt{magenta}, \texttt{yellow} or xcolor syntax (see \href{http://mirror.unicorncloud.org/CTAN/macros/latex/contrib/xcolor/xcolor.pdf}{here}). Can also be redefined globally (\texttt{pdbfDynamicTextColor})}
{\texttt{blue}}

\subsection{DataText}
Produce text from sql-statements.\\[3pt]
Example:\\[3pt]
The table ``test'' contains \dataText{SELECT COUNT(*) FROM test;} tuples.\\
The table ``test'' contains the following tuples: \dataText{SELECT * FROM test;}.\\[3pt]
%
\noindent Macros: \\[3pt]
\verb|\dataText{query}| \\[8pt]

\noindent Options: \\[3pt]

\option
{color}
{The textcolor of the displayed text.}
{\texttt{white}, \texttt{black}, \texttt{red}, \texttt{green}, \texttt{blue}, \texttt{cyan}, \texttt{magenta}, \texttt{yellow} or xcolor syntax (see \href{http://mirror.unicorncloud.org/CTAN/macros/latex/contrib/xcolor/xcolor.pdf}{here}). Can also be redefined globally (\texttt{pdbfDynamicTextColor})}
{\texttt{blue}}

\section{F.A.Q.}
\begin{itemize}
\item Q.: The overlay is not on the right position.\\
A.: Most likely you use pages with different sizes in your document. This is currently not supported by PBDF 
\item Q.: I get \verb|Error: paperwidth value missing! Did you forgot to specify the| \\ \verb|papersize via the geometry package?| when compiling my document.\\
A.: You need to explicitly specify the papersize of your document via the geometry package (e.g. \verb|\usepackage[letterpaper]{geometry}|)
\item Q.: I get \verb|\unhbox \voidb@x \bgroup \let \unhbox \voidb@x \setbox \@tempboxa \hbox| \verb|{u\global \mathchardef \accent@spacefactor \spacefactor }\accent 127 u\egroup| \newline \verb|\spacefactor \accent@spacefactor| or a similar string in a error message.\\
A.: Chances are high that you use the \verb|\usepackage[utf8]{inputenc}| package or a similar package. These are not fully compatible with PDBF. If you really have to use the utf8 package then you cant use special characters inside options and queries of the PDBF package.
\end{itemize}
